---
title: "Supporting materials: Forecasting the words of later self-descriptions"
format:
  html:
    embed-resources: true
    toc: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
r <- function(f) read_csv(file.path("results",f),show_col_types=FALSE)
tab <- function(f,digits=4) knitr::kable(r(f),digits=digits)
```

## Sample and missingness

All tables refer to the 200 public pairs unless otherwise indicated. Missing
categorical predictors are encoded as a separate level. Follow-up demographic
fields are never used as predictors.

```{r}
tab("sample_summary.csv",2)
tab("ethnicity.csv",0)
tab("demographic_completeness.csv",0)
```

## Whole-response paired contrasts

Differences are within participant; positive values favor repeating the
participant's earlier text. Intervals are percentile bootstrap intervals.

```{r}
tab("text_forecast_contrasts.csv")
```

## Probability scores and paired contrasts

All-person Brier loss includes all participants. Conditional metrics omit a
participant if their relevant word stratum is empty. Average precision omits
participants without a positive word in the relevant target set. None of these
omissions affects Brier loss across the full vocabulary. `ap_absent` evaluates
only words absent at baseline. Positive Brier contrasts favor the second model;
positive AP contrasts favor the population model because the contrast is always
population minus model.

```{r}
tab("word_score_summary.csv")
tab("word_brier_contrasts.csv",6)
tab("innovation_contrasts.csv",6)
```

## Vocabulary and fold checks

Vocabularies use training follow-up document frequency only. Targets can differ
between folds, so these are not fixed universal vocabulary scores. Coverage is
the fraction of later unique content words included. Increasing the threshold
changes the population of words as well as prediction difficulty; compare
models within a threshold, not raw Brier values across thresholds.

```{r}
tab("fold_diagnostics.csv")
tab("vocabulary_sensitivity.csv")
```

## Partition sensitivity and original source split

These checks were added after the initial analysis. Each alternative partition
again excludes the evaluated participant from all fitting. Repeated partitions
are not independent samples and their range is not a confidence interval. Only
population and transition forecasts are refitted here. The fixed original split
fits on the 150 public training pairs and evaluates the 50 development pairs;
these are the same people already included in the main cross-validation.

```{r}
tab("partition_sensitivity.csv",6)
tab("original_split_summary.csv",6)
```

## Ridge tuning

Each row records the average inner-validation squared loss at a candidate
penalty. Input scaling and both input and output vocabularies are fitted inside
each inner training split. Three inner folds are shared across feature models
within each outer fold. The selected penalty is common across words. The dual
ridge solution uses $(XX^{T}+n\lambda I)^{-1}$ with centered outcomes; fitted
intercepts are their training means. Predictions are clipped before scoring.

```{r}
r("tuning.csv") |> filter(selected) |> knitr::kable(digits=5)
```

## Calibration

Bins pool held-out participant–word predictions and therefore contain dependent
observations. These descriptive summaries are not independent binomial trials
and have no binomial confidence intervals. A model can be well calibrated on
average while discriminating poorly between individuals.

```{r}
tab("calibration.csv")
```

## Frequent-word transitions

Rows below have at least 30 baseline mentions among the folds in which they
were eligible. `n` can differ across words because eligibility is fold-specific.
These are descriptive estimates on evaluated outcomes, not fitted model
parameters or confirmatory comparisons between identity domains. Word meanings
and context are not adjudicated.

```{r}
r("word_transitions.csv") |> filter(baseline_present>=30) |> knitr::kable(digits=3)
```

## Computation and verification

All data work and figures use R and tidyverse conventions. Original files are
preserved and hash-checked. The protocol, source search record, and complete
participant-level prediction files accompany the article. The stop list is
specified directly in `analysis/helpers.R`; no external dictionary or language
model is required. R's default Mersenne-Twister generator is seeded with
20260925 for the primary analyses; alternative partitions use the seeds shown.

```{r}
cat(paste(readLines("results/verification.txt"),collapse="\n"))
```

```{r}
cat(paste(readLines("results/sessionInfo.txt"),collapse="\n"))
```
